\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvtheme[burgundy]{banking}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[margin=.85in, scale=0.8]{geometry}
\recomputelengths
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tabularx}


\AfterPreamble{
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
}

%pretty C++
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize ++}}

%pretty C#
\newcommand{\CS}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\#}}

\newcommand{\bitem}{\begin{samepage}\begin{itemize}[leftmargin=*, labelindent=8pt, itemsep=-1pt]}
\newcommand{\eitem}{\end{itemize}\end{samepage}}

\newcommand{\entry}[6]
{\cventry{#1}{#2}{#3}{#4}{#5}{
    \bitem 
    #6
    \eitem
    }
}

\newcommand{\itemc}[5]
{\cventry{#4}{#1}{#2}{#3}{}{#5}
}



%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

% personal data
\firstname{Bill}
\familyname{Engels}
%\address{1900 NE 68th St}{98115 Seattle, WA}
\email{w.j.engels@gmail.com}
\phone{503-740-7435}
\homepage{github.com/bwengals}
 

\begin{document}
\maketitle
\vspace*{-5mm}
\section{Relevant Experience}
    \entry{10/2014 -- 8/2016}{Member of Technical Staff}{Open Data Group}{River Forest, IL}{}{
		\item[--] Worked on an assortment of behavioral models for computer network traffic.  Developed and implemented a
		set of Hadoop and Spark jobs (aggregations, regressions, clustering) that searched for anomalous behavior in terabyte-scale data.
        \item[--] Created suite of dynamic visualizations of live data streams (D3.js) and static daily reports summarizing analytics (\LaTeX, HTML, Matplotlib).
        \item[--] Helped industrial data science client productionalize their machine learning models (e.g. gradient boosted trees, logistic regressions).
		\item[--] Software development for the Hadrian analytics engine,
		including the prediction methods of common machine learning models such
		as SVMs, GLMs, Naive Bayes and basic Neural Nets, exporter for objects produced by R's \textit{gbm} package, also the library of probability distributions, CDFs, and QFs and associated unit-tests and documentation.
    }
    \entry{2012 -- 6/2016}{Guest member of Caltech CaRT group, University of Oregon}{LIGO Scientific Collaboration}{}{}{
	  \item[--] Bayesian approach parameter estimation on uncertain supernova signals buried in noisy LIGO detector data.
		  Publication in preparation. 
	  \item[--] Author on \href{http://journals.aps.org/prl/abstract/10.1103/PhysRevLett.116.061102}{first gravitational wave detection paper}, Phys. Rev. Lett. 2016.
      \item[--] \href{https://arxiv.org/abs/1406.1164}{First author publication, Phys. Rev. D. 2014.} A multivariate multiple regression analysis of complex-valued simulation data.
	  \item [--] Presentations: \href{http://ccom.ucsd.edu/~pcgm31/}{PCGM31, March 2015}, Caltech Supernova group, July 2014
		}
\closesection{}

\section{Open Source Contributions}
    \entry{}{Probabilstic Programming}{\href{https://github.com/pymc-devs/pymc3}{PyMC3}}{}{}{
        \item[--] Contributor, Gaussian Process covariance functions
    }

    \entry{}{High performance histogram-style data aggregations in distributed environments}{\href{https://github.com/histogrammar/histogrammar-python}{Histogrammar (Python)}}{}{}{
        \item[--] Matplotlib built-in plotting methods.
    }
\closesection{}

\section{Skills}

\cvitem{Programming}{Python, R, Scala, Matlab}
\cvitem{Statistical}{EDA, Regression Analysis, clustering, Bayesian modeling, algorithm implementation}
\cvitem{Technology}{Git, SQL, AWS, Spark, Hadoop, D3.js, Linux}
\closesection{}

\section{Education} 
    \cventry{2013}{Physics}{University of Oregon}{B.S.}{}{}
%    \cventry{starting 9/2017}{MS Statistics}{Portland State University}{}{}{}
\end{document}
